---
title: "Shootings Analysis"
output: html_document
---

```{r setup, include = TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('analysis.R')
library("knitr")
```
## Summary of Shootings in 2018
In 2018, a total of `r number_of_shootings` shootings occurred in 
the United States. A total of `r number_lives_lost` people were 
lost and the city most impacted (impact is measured as the sum of 
victims killed and victims injured) was `r most_impacted_city`. 
Further analysis was done broadly dividing the United States into 
two reigons; West and East of the Mississippi. The longitude used 
to create the reigons was -90 degrees. East of the Mississippi, the impact score totaled, `r east_of_the_mississppi`. West of the
Mississippi scored, `r west_of_the_mississppi`. There were
significantly more shootings that occured East of the Mississippi.

## Summary Table
```{r sum_table, echo=FALSE}
kable(sum_table)
```

## Parkland
On `p_date`, Nikolas Cruz open fired on Marjory Stoneman Douglas High School. He killed `p_killed` and injured `p_injured`. A total of `p_damage` were affected by his actions. This number however is not representative of the greater impact of Cruz's action. Not included in this analysis are the grieving families and members of the greater Parkland community. Cruz was previously expelled from Marjory Stoneman Douglas High School and was living with a foster family after the death of his mother. He was astranged from his father.
URL: https://www.nbcnews.com/news/us-news/police-respond-shooting-parkland-florida-high-school-n848101

## Map
```{r usa_plot, echo=FALSE}
usa_plot
```

## Damage vs. State Population
```{r state_and_pop, echo=FALSE}
state_and_pop
```

I chose this visual encoding layout becaue I think that it starkly
represents the how much shootings affect the country as a whole in
regards to the sheer size of the United States. One insight I
derived by this chart were that against the population of the
United States, shootings affect a very, very small percentage of
the overall population. The other insight I thought of, after
reviewing this chart, is that the impact of guns/shootings in the
United States is perhaps overstated by media outlets. Given that
they indeed do affect a very small percentage of Americans, why
are Americans spending so much time arguing about gun legislation?

