---
title: "Shootings Analysis"
output: html_document
---

```{r setup, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('analysis.R')
library("knitr")
```
## Summary of Shootings in 2018
In 2018, a total of `r number_of_shootings` shootings occurred in 
the United States. A total of `r number_lives_lost` people were 
lost and the city most impacted (impact is measured as the sum of 
victims killed and victims injured) was `r most_impacted_city`. 
Further analysis was done broadly dividing the United States into 
two reigons; West and East of the Mississippi. The longitude used 
to create the regions was -90 degrees. East of the Mississippi, the impact score totaled, `r east_of_the_mississppi`. West of the
Mississippi scored, `r west_of_the_mississppi`. There were
significantly more shootings that occured East of the Mississippi.

## Summary Table
```{r sum_table, echo=FALSE, warning=FALSE}
kable(sum_table)
```

Of the `r damage` total people directly affected by gun violence, `r top10_damage`% of those affected occured in the top ten states listed.

## Parkland
On `r p_date`, Nikolas Cruz open fired on Marjory Stoneman Douglas High School. He killed `r p_killed` and injured `r p_injured`. A total of `r p_damage` were affected by his actions. This number however is not representative of the greater impact of Cruz's action. Not included in this analysis are the grieving families and members of the greater Parkland community. Cruz was previously expelled from Marjory Stoneman Douglas High School and was living with a foster family after the death of his mother. He was astranged from his father.

URL: https://www.nbcnews.com/news/us-news/police-respond-shooting-parkland-florida-high-school-n848101

## Map
```{r usa_plot, echo=FALSE, warning=FALSE}
usa_plot
```

Two insights revealed by this map is that visually, there appear to me more instances of shootings occuring East of the Mississippi river and West of the Mississippi shootings usually occurred in large cities and not rural ones.

## Damage vs. State Population
```{r state_and_pop, echo=FALSE, warning=FALSE}
state_and_pop
```

I chose this visual encoding layout becaue I think that it starkly
represents the how much shootings affect the country as a whole in
regards to the sheer size of the United States. It does this by 
using color (or lack there of) and differences in length (or lack 
ther of). One insight I derived by this chart were that against 
the population of the United States, shootings affect a very, very
small percentage of the overall population. The other insight I 
thought of, after reviewing this chart, is that the impact of 
guns/shootings in the United States is perhaps overstated by media
outlets. Given that they indeed do affect a very small percentage of Americans, why are Americans spending so much time arguing 
about gun legislation?

